Diversity dynamics in Nymphalidae butterflies: Effect of phylogenetic uncertainty on diversification rate shift estimates

### 2015-01-22 MS_revised.tex
move tables to text
table 1

@@

% Table 1
\section*{Tables}
\begin{table}[!h]
\caption{\bf{Significant net diversification rate shifts found in the MEDUSA analysis of the Nymphalid maximum clade credibility tree.}}
\begin{tabular}{lccrrcl}
Shift N$^\circ$ & Shift.Node & Model & r          & LnLik.part & AICc     & Taxa                                                       \\
1               & 399        & yule  & 0.092459   & -1055.957  &          & Nymphalidae (root)                                         \\
2               & 691        & bd    & 0.054129   & -406.3703  &          & Limenitidinae + Heliconiinae                               \\
3               & 299        & yule  & 0.311199   & -6.3058    &          & \emph{Ypthima}                                             \\
4               & 224        & yule  & 0.290989   & -6.2601    &          & \emph{Charaxes}                                            \\
5               & 750        & yule  & 0.186913   & -147.4146  &          & Oleriina + Ithomiina + Napeogenina + Dircennina + Godyrina \\
6               & 405        & yule  & 0.116252   & -555.0276  &          & Satyrinae                                                   \\
7               & 495        & yule  & 0.064656   & -124.9143  &          & Coenonymphina                                              \\
8               & 609        & yule  & 0.240562   & -35.0908   &          & Phyciodina in part                                         \\
9               & 787        & bd    & 0.042332   & -43.7819   &          & Danaini in part                                            \\
10              & 231        & yule  & 0.209416   & -4.7955    &          & \emph{Coenonympha}                                         \\
11              & 478        & yule  & 0.311684   & -9.2218    &          & \emph{Caeruleuptychia} + \emph{Magneuptychia}              \\
12              & 659        & yule  & 0.219253   & -11.2686   &          & \emph{Callicore} + \emph{Diaethria}                        \\
13              & 444        & yule  & 0.220615   & -43.7812   &          & Satyrina                                                   \\
14              & 524        & yule  & 0.190754   & -26.0651   &          & Mycalesina                                                 \\
15              & 355        & yule  & 0.234041   & -6.2013    &          & \emph{Pedaliodes}                                          \\
16              & 714        & yule  & 0          & 0          &          & \emph{Dryas} + \emph{Dryadula}                             \\
17              & 377        & yule  & 0.311671   & -4.1986    &          & \emph{Taenaris}                                            \\
18              & 688        & yule  & 0.024724   & -17.5256   &          & Pseudergolinae                                             \\
19              & 583        & yule  & 0          & 0          & 5090.492 & \emph{Anaeomorpha} + \emph{Hypna}                                       
\end{tabular}
\begin{flushleft}Shift.Node=node number, Model=preferred diversification model by MEDUSA, r=net diversification rate, LnLik.part=log likelihood value.
\end{flushleft}
\end{table}

\pagebreak
\bibliography{refs}{}

>>>>

% Table 1
\begin{table}[!ht]
\begin{adjustwidth}{-2.25in}{0in}
\caption{{\bf Significant net diversification rate shifts found in the MEDUSA analysis of the Nymphalid maximum clade credibility tree.}}
\begin{tabular}{|l|c|c|r|r|c|l|}
\hline
Shift N$^\circ$ & Shift.Node & Model & r          & LnLik.part & AICc     & Taxa                                                       \\ \hline
1               & 399        & yule  & 0.092459   & -1055.957  &          & Nymphalidae (root)                                         \\ \hline
2               & 691        & bd    & 0.054129   & -406.3703  &          & Limenitidinae + Heliconiinae                               \\ \hline
3               & 299        & yule  & 0.311199   & -6.3058    &          & \emph{Ypthima}                                             \\ \hline
4               & 224        & yule  & 0.290989   & -6.2601    &          & \emph{Charaxes}                                            \\ \hline
5               & 750        & yule  & 0.186913   & -147.4146  &          & Oleriina + Ithomiina + Napeogenina + Dircennina + Godyrina \\ \hline
6               & 405        & yule  & 0.116252   & -555.0276  &          & Satyrinae                                                  \\ \hline
7               & 495        & yule  & 0.064656   & -124.9143  &          & Coenonymphina                                              \\ \hline
8               & 609        & yule  & 0.240562   & -35.0908   &          & Phyciodina in part                                         \\ \hline
9               & 787        & bd    & 0.042332   & -43.7819   &          & Danaini in part                                            \\ \hline
10              & 231        & yule  & 0.209416   & -4.7955    &          & \emph{Coenonympha}                                         \\ \hline
11              & 478        & yule  & 0.311684   & -9.2218    &          & \emph{Caeruleuptychia} + \emph{Magneuptychia}              \\ \hline
12              & 659        & yule  & 0.219253   & -11.2686   &          & \emph{Callicore} + \emph{Diaethria}                        \\ \hline
13              & 444        & yule  & 0.220615   & -43.7812   &          & Satyrina                                                   \\ \hline
14              & 524        & yule  & 0.190754   & -26.0651   &          & Mycalesina                                                 \\ \hline
15              & 355        & yule  & 0.234041   & -6.2013    &          & \emph{Pedaliodes}                                          \\ \hline
16              & 714        & yule  & 0          & 0          &          & \emph{Dryas} + \emph{Dryadula}                             \\ \hline
17              & 377        & yule  & 0.311671   & -4.1986    &          & \emph{Taenaris}                                            \\ \hline
18              & 688        & yule  & 0.024724   & -17.5256   &          & Pseudergolinae                                             \\ \hline
19              & 583        & yule  & 0          & 0          & 5090.492 & \emph{Anaeomorpha} + \emph{Hypna}                          \\ \hline
\end{tabular}
\begin{flushleft}Shift.Node=node number, Model=preferred diversification model by MEDUSA, r=net diversification rate, LnLik.part=log likelihood value.
\end{flushleft}
\label{table1}
\end{adjustwidth}
\end{table}

@@

\bibliography{refs}{}
